Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2019-06-10 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
fixed references file

\documentclass[AMS,STIX2COL]{WileyNJD-v2}
\usepackage{natbib}
\usepackage{amsmath,amsfonts}

@@

The forensics sciences and the heath care industry are two areas that have benefitted from machine learning but have an obvious need for explainable predictions. For example, \citet{aoas} discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun. Yu, Beam, and Kohane (2018) describe how healthcare has advanced through the use of machine learning in various ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes. In \hh{both} of these cases, the decisions made based on the results of the machine learning models can greatly impact the lives of human beings. If it is not possible to explain the output from a model, it becomes questionable whether the results from the model can be trusted to make important decisions.

@@

\section*{Acknowledgments}
This is acknowledgment text~\cite{Elbaum2002}. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here.

@@

%\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
\bibliography{wileyNJD-AMS}%

>>>>

\documentclass[AMS,STIX2COL]{WileyNJD-v2}
\usepackage{natbib}
%\bibliographystyle{asa}

\usepackage{amsmath,amsfonts}

@@

The forensics sciences and the heath care industry are two areas that have benefitted from machine learning but have an obvious need for explainable predictions. For example, \citet{aoas} discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun. \citet{yu:2018} describe how healthcare has advanced through the use of machine learning in various ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes. In \hh{both} of these cases, the decisions made based on the results of the machine learning models can greatly impact the lives of human beings. If it is not possible to explain the output from a model, it becomes questionable whether the results from the model can be trusted to make important decisions.

@@

\section*{Acknowledgments}
This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here.

@@

%\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
\bibliography{references}%
